Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
vobj: example

\input{nuobj}

@@

>>>>

\input{macros}
\input{nuobj}

@@

\begin{frame}[fragile]{${\nu}Obj$: Example (encoding of monomorphic functions)}
A $\lambda$-abstraction $\lambda ( x : T )\; t$ is represented as a
class with an abstract member \code!arg! for the function argument:
\begin{lstlisting}
[x: {arg: T}| fun = [res = $t'$]]
\end{lstlisting}
$t'$ corresponds to term $t$ in which all occurrences of $x$ are
replaced by \code!$x$.arg!. We cannot directly access \code!arg! on
the right-hand side of \code!fun!: this wouldn't be ``contractive'',
because \code!arg! might not be initialized before \code!fun!. Hence,
we pack $t'$ in another class to ensure contractiveness. Now, an
application $g(e)$ gets decomposed into three subsequent steps:
\begin{lstlisting}
$\nu\,$g$_{app}$  <- g & [arg = e];
$\nu\,$g$_{eval}$ <- g$_{app}$.fun;
g$_{eval}$.res
\end{lstlisting}
First we instantiate function \code!g! with a concrete argument
yielding a thunk \code!g$_{app}$!. Then we evaluate this thunk by
creating an instance \code!g$_{eval}$! of it. Finally we extract the
result by querying field \code!res! of \code!g$_{eval}$!.
\end{frame}
